Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite

### 2021-05-04 paper2020/paper.tex
deanon + citation fix

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\title{Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite }
% \author{\ifanon Anonymous for review\else
%   \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
%   \affiliation{University of Gothenburg}
%   \email{firstname.lastname@gu.se}\fi}

\author{\ifanon Anonymous for review\else
  {Jean-Philippe Bernardy}\footnote{University of Gothenburg} ~~ {Stergios Chatzikyriakidis}\footnote{University of Gothenburg}
}

@@

\vspace{-1.5ex}
\begin{equation}
  \label{eq:smith-novel-1}
\begin{array}{l}
∀x. novel(x) ∧ \\
∃t_1,t_2. [t_1,t_2] ⊆ 1991 ∧ write(smith,x,t_1,t_2) ∧ \\
∃t_3,t_4. [t_3,t_4] ⊆ 1992 ∧ write(smith,x,t_3,t_4) \\
⟶ ⊥ \\
\end{array}
\end{equation}
Note here that the scope for the existential is extended beyond the
scope of \textbf{P1}, and its polarity switched (to universal). This extension can follow the account of
\citet{unger_dynamic_2011}, and our implemented analysis of
anaphora\ifanon (citation anonymized)
\else\citep{bernardy_computational_2018,bernardy_wide-coverage_2019}\fi.

>>>>

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\title{Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite}
% \author{\ifanon Anonymous for review\else
%   \authorname{Jean-Philippe Bernardy} \authorname{Stergios Chatzikyriakidis}
%   \affiliation{University of Gothenburg}
%   \email{firstname.lastname@gu.se}\fi}

\author{
  Jean-Philippe Bernardy    \quad\quad\quad
  Stergios Chatzikyriakidis \\
  Centre for Linguistic Theory and Studies in Probability \\
  Department of Philosophy, Linguistics and Theory of Science \\ University of Gothenburg \\
  \texttt{firstname.lastname@gu.se} \\
}

@@

\vspace{-1.5ex}
\begin{equation}
  \label{eq:smith-novel-1}
\begin{array}{l}
∀x. novel(x) ∧ \\
∃t_1,t_2. [t_1,t_2] ⊆ 1991 ∧ write(smith,x,t_1,t_2) ∧ \\
∃t_3,t_4. [t_3,t_4] ⊆ 1992 ∧ write(smith,x,t_3,t_4) \\
⟶ ⊥ \\
\end{array}
\end{equation}
Note here that the scope for the existential is extended beyond the
scope of \textbf{P1}, and its polarity switched (to universal). This extension can follow the account of
\citet{unger_dynamic_2011}, and our implemented analysis of
anaphora\ifanon (citation anonymized)
\else\citep{bernardy_computational_2020,bernardy_wide-coverage_2019}\fi.
